The formal verification of the ctm approach to forcing \thanks{Supported by Secyt-UNC projects 33620180100855CB and 33620180100465CB, and Conicet.}

### 2022-10-25 Independence_CH/related.tex
Repeated words

Concerning the minimum amount of Replacement needed to construct
forcing extensions, only recently we learned about Mathias' work on the
subject (for which a summary is offered in
\cite[Sect.~6]{kanamori-mathias}). In
\cite[Sect.~1]{mathias:hal-01188043}, models $M$ of Zermelo Set Theory
are offered for which each of the inclusions $M\subseteq M[G]$ and
$M\supseteq M[G]$ fail, where the poset $\pP$ is the trivial $\{\1
\}$. In one of them, $K$, we have $\om\in K \sm K[G]$, hence the
ordinals do not coincide.

>>>>

Concerning the minimum amount of Replacement needed to construct
forcing extensions, only recently we learned about Mathias' work on the
subject (for which a summary is offered in
\cite[Sect.~6]{kanamori-mathias}). In
\cite[Sect.~1]{mathias:hal-01188043}, models $M$ of Zermelo Set Theory
are constructed for which each of the inclusions $M\subseteq M[G]$ and
$M\supseteq M[G]$ fail, where the poset $\pP$ is the trivial $\{\1
\}$. In one of them, $K$, we have $\om\in K \sm K[G]$, hence the
ordinals do not coincide.
